Box

### 2021-07-14 MS/box.Rmd
think I see the dumb error I made in ox 1 SMD equation, maybe fixed now
equation fixed
Fixed a rogue X to M

$$
\sigma^2(aX_1 \pm b)=a^2 * \sigma^2_{X_{1}}
$$

@@

$$
s_{SMD_{T}}^2 = \left(\frac{1}{{T_{2} - T_{1}}}\right)^2 +  \frac{N_{1} + N_{2}}{N_{1}N_{2}}  + \frac{SMD_{T}^2}{2\left( N_{1} + N_{2}\right)}
$$

@@

$$
\sigma^2_{ln{RR}} \approx  \left ( \frac{SD_{1}^2}{N_{1}}\right ) * \left(\frac{1}{M_{1}} \right)^2 + \left ( \frac{SD_{2}^2}{N_{2}}\right ) * \left(\frac{1}{M_{2}} \right)^2 =   \left ( \frac{SD_{1}^2}{N_{1}M_{1}^2}\right ) + \left ( \frac{SD_{2}^2}{N_{2}M_{2}^2}\right )
$$
Note here again that the first term, $\frac{SD_{1}^2}{N_{1}}$ is the sampling variance for group 1, and we simply multiply this term by the square of the first derivative of $X_{1}$ as the Delta method tells us. Of course, readers will see that this is equivalent to the sampling variance for $ln_{RR}$ (Table 1). We can extend this sampling variance to include dependency between the groups as:

>>>>

$$
\sigma^2(aM_1 \pm b)=a^2 * \sigma^2_{M_{1}}
$$

@@

$$
s_{SMD_{T}}^2 = \left (\frac{N_{1} + N_{2}}{N_{1}N_{2}}  + \frac{SMD_{T}^2}{2\left( N_{1} + N_{2}\right)} \right) \left(\frac{1}{{T_{2} - T_{1}}}\right)^2
$$

@@

$$
\sigma^2_{ln{RR}} \approx  \left ( \frac{SD_{1}^2}{N_{1}}\right ) * \left(\frac{1}{M_{1}} \right)^2 + \left ( \frac{SD_{2}^2}{N_{2}}\right ) * \left(\frac{1}{M_{2}} \right)^2 =   \left ( \frac{SD_{1}^2}{N_{1}M_{1}^2}\right ) + \left ( \frac{SD_{2}^2}{N_{2}M_{2}^2}\right )
$$
Note here again that the first term, $\frac{SD_{1}^2}{N_{1}}$ is the sampling variance for group 1, and we simply multiply this term by the square of the first derivative of $M_{1}$ as the Delta method tells us. Of course, readers will see that this is equivalent to the sampling variance for $ln_{RR}$ (Table 1). We can extend this sampling variance to include dependency between the groups as:
